Trends of SDR in Thessaloniki

### 2023-09-02 Article.Rmd
Commit 2023-09-02 19:09

Similar to the long term trends discussed above, we have produced the deseasonalized trend for the different sky conditions, for each season of the year, using the corresponding mean monthly values.

While in Spring and Summer the brightening of the SDR seem to be very low, although the statistical significance is now adequate for all cases, there are significant changes in Winter and Autumn
(Figure\ \ref{fig:seasonalALL} and Table\ \ref{tab:trendseasontable}).
Especially for winter and

This can give us a better understanding of the annual cycle of the trends.

@@

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("SDR" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp)          <- NULL
names(pp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Statistical signif. [%]")
## order by season
target    <- c("Winter", "Spring", "Summer", "Autumn")
new_order <- sapply(target, function(x,pp){which(pp$Season == x)}, pp=pp)
which(pp)
pp        <- pp[new_order,]
## numeric precision
pp$`Trend [%/year]`          <- signif(pp$`Trend [%/year]`, 3)
pp$`Trend p-value`           <- signif(pp$`Trend p-value`,  3)
pp$`Statistical signif. [%]` <- signif(pp$`Statistical signif. [%]`,  3)

rownames(pp) <- NULL

# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(pp,
       justify = c('center', 'center', 'right', 'right', 'center'),
       split.table = Inf,
       caption = "\\label{tab:trendseasontable}SDR trends of monthly anomaly for each season of the year.")
```
<!-- \normalsize -->

<!--
## Consistency of the trends

A method to evaluate changes in the long term trend is to use the cumulative sum of the variable.

Figure\ \ref{fig:cumsum}

... different in aggregation ...
-->

@@

>>>>

Similar to the long term trends discussed above, we have produced the deseasonalized trend for the different sky conditions, for each season of the year, using the corresponding mean monthly values
(Figure\ \ref{fig:seasonalALL} and Table\ \ref{tab:trendseasontable}).
For All-sky condition the brightening of SDR is very significant for the Winter, close to the long term trend for the Autumn, and almost four times lower than the long term trend for Sprint and Summer, indicating a relation to the cloud pattern of each season.
Moreover when examining the Clear- and Cloud-sky conditions the trends between these condition are are almost complementary to each other for Winter and Autumn respectively. On the latter cases during Spring and Summer the statistical significance along with the actual trend are very low for a meaningful comparison.

@@

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep         = ";",
               header      = TRUE)
pp <- pp[grep("SDR" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp)          <- NULL
names(pp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Statistical signif. [%]")
## order by season
target    <- c("Winter", "Spring", "Summer", "Autumn")
new_order <- sapply(target, function(x,pp){which(pp$Season == x)}, pp = pp)
pp        <- pp[new_order,]
## put all sky first
A  <- which(pp$`Sky condition` == "All sky cond.")
B  <- which(pp$`Sky condition` != "All sky cond.")
pp <- pp[c(A,B),]
## numeric precision
pp$`Trend [%/year]`          <- signif(pp$`Trend [%/year]`, 3)
pp$`Trend p-value`           <- signif(pp$`Trend p-value`,  3)
pp$`Statistical signif. [%]` <- signif(pp$`Statistical signif. [%]`,  3)

## arrange columns
pp <- pp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]", 
      "Trend p-value", 
      "Statistical signif. [%]"
      )]

rownames(pp) <- NULL
# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(pp,
       justify = c('right', 'right', 'right', 'right', 'center'),
       split.table = Inf,
       caption = "\\label{tab:trendseasontable}SDR trends of monthly anomaly for each season of the year.")
```
<!-- \normalsize -->

<!--
## Consistency of the trends
-->

@@

Brightening is driven during Winter and Summer
